NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-09-07 Manuscript/manuscriptPS.tex
Add corrected MacRog simulations by M. Javanainen: http://nmrlipids.blogspot.com/2018/07/nmrlipids-iv-first-draft-of-manuscript.html?showComment=1535364446749#c4563235956514366812

    POPC:OPPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0    & 0   & 120:24 & 5760 & 0    & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:OPPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0    & 0.10 & 120:24 & 5760 & 10   & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:OPPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0    & 0.30 & 120:24 & 5760 & 31   & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:OPPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0    & 1.00   & 120:24 & 5760 & 104  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:OPPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0    & 3.00   & 120:24 & 5760 & 311  & 298  & 200 & 200 \todoi{Equilibration?} & \cite{POPCpopsMACROG}  \\
    POPC:OPPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0.50  & 0   & 120:24 & 5760 & 52   & 298  & 200 & 190 & \cite{POPCpopsMACROGwithK}  \\
    POPC:OPPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &1.00    & 0   & 120:24 & 5760 & 104  & 298  & 200 & 190 & \cite{POPCpopsMACROGwithK}  \\
    POPC:OPPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &2.00    & 0   & 120:24 & 5760 & 208  & 298  & 200 & 145 & \cite{POPCpopsMACROGwithK}  \\
    POPC:OPPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &3.00    & 0   & 120:24 & 5760 & 311  & 298  & 200 & 125 & \cite{POPCpopsMACROGwithK}  \\
    POPC:OPPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &4.00    & 0   & 120:24 & 5760 & 415  & 298  & 200 & 125 & \cite{POPCpopsMACROGwithK}  \\

@@

\begin{figure*}[]
  \centering
  \includegraphics[width=18cm]{../Figs/CHANGESwithCaClPS.eps}
  \caption{\label{changesWITHCaClPS}
    Changes of POPC (left) and POPS (right) headgroup order parameters from POPC:POPS (5:1) mixture
    as a function CaCl$_2$ concentration from experiments \citenum{roux90} and different simulations
    at 298K (except the data for Berger model is from simulation of POPC:POPS (4:1) mixture at 310K \cite{ollila07a,melcrova16}). 
    The order parameter values from systems without calcium are set as the zero point of y-axis,
    except for the $\alpha$-carbon order parameter of POPS (bottom, right) for which the both order parameters are shifted
    such that the lower order parameter is zero without additional ions to correctly illustrate
    the forking with different concentrations of calcium.
    Potassium counterions are used in MacRog simulations and sodium counterions in Lipid14/17 simulations.
    In CHARMM36 and Berger simulation with added calcium, the charge is neutralized with calcium and monovalent counterions are not present.
  }
  \todo{Upcoming simulations with original CHARMM36 have been mentioned in the blog:
  http://nmrlipids.blogspot.com/2017/12/nmrlipids-iv-current-status-and.html?showComment=1520090718976\#c5569269391707740056} \\
  \todo{Upcoming Lipid17 simulations have been mentioned in the blog
    http://nmrlipids.blogspot.com/2017/12/nmrlipids-iv-current-status-and.html?showComment=1515177306419\#c994825612316235467}
\end{figure*}

\begin{figure}[]
  \centering
  \includegraphics[width=9cm]{../Figs/CAdensPCPSmixture.eps}
  \caption{\label{CAdensPCPSmixture}
    Ca2+ density profiles from simulations.
  }
  \todo{The CHARMM results are mass densities, numbers should be used.} \\
  \todo{Should we include also counterions into the plot?} \\
  \todo{Not all the data from MacRog is included.} 
\end{figure}

>>>>

    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0    & 0   & 120:24 & 5760 & 0    & 298  & 400 & 250 & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0    & 0.10 & 120:24 & 5760 & 10   & 298  & 600 & 300 & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0    & 0.30 & 120:24 & 5760 & 31   & 298  & 600 & 300  & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0    & 1.00   & 120:24 & 5760 & 104  & 298  & 600 & 300  & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0    & 3.00   & 120:24 & 5760 & 311  & 298  & 600 & 300  & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0.50  & 0   & 120:24 & 5760 & 52   & 298  & 300 & 200 & \cite{POPCpopsMACROGwithK}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &1.00    & 0   & 120:24 & 5760 & 104  & 298  & 300 & 200 & \cite{POPCpopsMACROGwithK}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &2.00    & 0   & 120:24 & 5760 & 208  & 298  & 300 & 200 & \cite{POPCpopsMACROGwithK}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &3.00    & 0   & 120:24 & 5760 & 311  & 298  & 300 & 200 & \cite{POPCpopsMACROGwithK}  \\
%    POPC:OPPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &4.00    & 0   & 120:24 & 5760 & 415  & 298  & 300 & 200 & \cite{POPCpopsMACROGwithK}  \\

@@

\begin{figure*}[]
  \centering
  \includegraphics[width=18cm]{../Figs/CHANGESwithCaClPS.eps}
  \caption{\label{changesWITHCaClPS}
    Changes of POPC (left) and POPS (right) headgroup order parameters from POPC:POPS (5:1) mixture
    as a function CaCl$_2$ concentration from experiments \citenum{roux90} and different simulations
    at 298K (except the data for Berger model is from simulation of POPC:POPS (4:1) mixture at 310K \cite{ollila07a,melcrova16}). 
    The order parameter values from systems without calcium are set as the zero point of y-axis,
    except for the $\alpha$-carbon order parameter of POPS (bottom, right) for which the both order parameters are shifted
    such that the lower order parameter is zero without additional ions to correctly illustrate
    the forking with different concentrations of calcium.
    Potassium counterions are used in MacRog simulations and sodium counterions in Lipid14/17 simulations.
    In CHARMM36 and Berger simulation with added calcium, the charge is neutralized with calcium and monovalent counterions are not present.
  }
  \todo{Upcoming simulations with original CHARMM36 have been mentioned in the blog:
  http://nmrlipids.blogspot.com/2017/12/nmrlipids-iv-current-status-and.html?showComment=1520090718976\#c5569269391707740056} \\
\end{figure*}

\begin{figure}[]
  \centering
  \includegraphics[width=9cm]{../Figs/CAdensPCPSmixture.eps}
  \caption{\label{CAdensPCPSmixture}
    Ca2+ density profiles from simulations.
  }
  \todo{The CHARMM results are mass densities, number densities should be used when the data by Jesper Madsen is available.} \\
  \todo{Should we include also counterions into the plot?} \\
\end{figure}
